Opportunities for improvement in adult trauma patients admitted to the intensive care unit: A registry-based study

### 2024-01-11 manuscript.Rmd

Abstract
========
Background
----------
Trauma is a leading cause of mortality and morbidity worldwide. A cornerstone in developing the trauma quality improvement programs is multidisciplinary mortality and morbidity review. The purpose of these is to identify opportunities for improvement (OFI), which are necessary in order to implement corrective actions. Many patients with severe trauma is admitted to the intensive care unit (ICU), but little is known about opportunities for improvement in this group of patients. The aim of this study is to characterise OFI in adult trauma patients admitted to the ICU and assess how patient factors are associated with OFI in these patients.

@@

Setting
-------
The Karolinska University Hospital in Solna is a level 1 trauma centre based on the definition by the American College of Surgeons (ACS) Committee on Trauma [5], and is designated to receive all patients in Stockholm with major or suspected major trauma. The hospital has direct access to radiology, surgery, emergency medicine, intensive care and consultants from relevant specialities [6]. All patients are included in a mortality and morbidity screening combining individual review and specific audit filters by specialized nurses. The patients who are identified as having higher probability for OFI are discussed in a multidisciplinary conference held every 6-8 weeks. Examples of OFI include the need for better organization or more senior members taking part in the trauma care. The presence or absence of OFI is decided among the participants of the conference and then recorded in the trauma care quality database.

@@

Variables and data sources/measurements
---------------------------------------

### Study outcome
The study outcome will be on the presence of OFI in adult patients treated in the ICU focusing on different types of opportunities for improvement including delayed treatment, judgement error and technical errors...

>>>>

Abstract
========

Background
----------
Trauma is a leading cause of mortality and morbidity worldwide. A cornerstone in developing the trauma quality improvement programs is multidisciplinary mortality and morbidity review. The purpose of these is to identify opportunities for improvement (OFI), which are necessary in order to implement corrective actions. Many patients with severe trauma is admitted to the intensive care unit (ICU), but little is known about opportunities for improvement in this group of patients. The aim of this study is to characterise OFI in adult trauma patients admitted to the ICU and assess how patient factors are associated with OFI in these patients.

@@

@@

Variables and data sources/measurements
---------------------------------------
### Study outcome
The study outcome will be on the presence of OFI in adult patients treated in the ICU focusing on different types of opportunities for improvement including delayed treatment, judgement error and technical errors...
